Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-04-02 talk/icooolps2009/paper.tex
Kill one comment by maciek that I addressed, and one that I think is wrong.

\fijal{RPython tracer operates on a level which is slightly higher level than
of the underlaying C. To be more precise: it operates on exception-transformed,
non-gc-transformed graphs with an extra bit of abstraction inversion that
finds out operations on loops and dicts, not sure how to express this}

@@

\fijal{This is wrong. Without virtuals there is also at most one assembler
loop per user loop. If it has more branches, we enter the loop as usual and
then we create a bridge for a new situation}
The condition for reusing already existing machine code needs to be adapted to
this new situation. In a classical tracing JIT there is at most one piece of
assembler code per loop of the jitted program, which in our case is the language
interpreter. When applying the tracing JIT to the language interpreter as
described so far, \emph{all} pieces of assembler code correspond to the bytecode
dispatch loop of the language interpreter. They correspond to different
unrollings and paths of that loop though. To figure out which of them to use
when trying to enter assembler code again, the program counter of the language
interpreter needs to be checked. If it corresponds to the position key of one of
the pieces of assembler code, then this assembler code can be entered. This
check again only needs to be performed at the backward branches of the language
interpreter.

>>>>

@@

The condition for reusing already existing machine code needs to be adapted to
this new situation. In a classical tracing JIT there is at most one piece of
assembler code per loop of the jitted program, which in our case is the language
interpreter. When applying the tracing JIT to the language interpreter as
described so far, \emph{all} pieces of assembler code correspond to the bytecode
dispatch loop of the language interpreter. They correspond to different
unrollings and paths of that loop though. To figure out which of them to use
when trying to enter assembler code again, the program counter of the language
interpreter needs to be checked. If it corresponds to the position key of one of
the pieces of assembler code, then this assembler code can be entered. This
check again only needs to be performed at the backward branches of the language
interpreter.
